Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-16 manuscript.tex
discussion

\dataavailability{This works is made reproducible using the following tools. First the manuscript's source code, and the code reproducing all figures is available on \href{https://github.com/SpikeAI/XXX}{GitHub}~\citep{Grimaldi2022review}. The paper is available as an \href{https://arxiv.org/abs/YYYY.XXX}{arXiv preprint} with links to previous versions. Find the associated \href{https://www.zotero.org/groups/4562620/polychronies}{zotero group} which was used to regroup relevant literature on the subject.}

\acknowledgments{We would like to thank Jean-Nicolas Jérémie, Hugo Ladret for useful discussions while writing this review.}

>>>>

\dataavailability{This works is made reproducible using the following tools. First the manuscript's source code, and the code reproducing all figures is available on \href{https://github.com/SpikeAI/XXX}{GitHub}. %~\citep{Grimaldi2023review}. 
The paper is available as an \href{https://arxiv.org/abs/YYYY.XXX}{arXiv preprint} with links to previous versions. Find the associated \href{https://www.zotero.org/groups/4562620/polychronies}{Zotero group} which was used to regroup relevant literature on the subject.}

\acknowledgments{We would like to thank Jean-Nicolas Jérémie, George Abitbol and Hugo Ladret for useful discussions while writing this review.}
